CRUSE to Safe Cycling in Ireland

### 2023-09-29 paper.qmd
Complete abstract tweaks
Shorten bit about car dependency

  For investment in cycling to deliver on the huge potential benefits cycling must become safer.
  With growth in the E-bike market, the tool will help inform inter-urban and rural networks to support the transfer of trips to sustainable modes for longer journeys.
  The findings and resulting tool are directly relevant to addressing the challenges and opportunities faced by National Road Authorities (NRAs) across Ireland.
  The provision of open access evidence, that can be used non-experts and professionals, is relevant to countries with sustainable transport policies worldwide.
keywords: 
  - Cycling
  - Open-source
  - Road Safety
  - Active Travel
date: last-modified
---

@@

Transport is responsible for 23% of global emissions, 70% of which is from road transport, nearly half of which (around 10% of global emissions) is from passenger cars [@jaramillo2022].
The transport system encourages, enables and in some cases enforces unsustainable lifestyles, including over-consumption of goods due to excessive mobile storage space and dependency on services that are only accessible by car due to land use plans that have built up around roads [@gray2001; @shergold2012; @motte-baumvol2010].

>>>>

  For investment in cycling to deliver on the huge potential benefits, cycling must become safer.
  With growth in the E-bike market, the tool will help inform inter-urban and rural networks to support the transfer of trips to sustainable modes for longer journeys.
  The findings and resulting tool are directly relevant to addressing the challenges and opportunities faced by National Road Authorities (NRAs) across Ireland.
  The provision of open access evidence, that can be used non-experts and professionals, is relevant to countries with sustainable transport policies worldwide.
keywords: 
  - Cycling
  - Open-source
  - Road Safety
  - Active Travel
date: last-modified
---

@@

Transport is responsible for 23% of global greenhouse gas emissions, 70% of which are from road transport, nearly half of which (around 10% of global emissions) is from passenger cars [@jaramillo2022].
The transport system encourages, enables and in some cases enforces unsustainable lifestyles.
Services that are only accessible by car lock-in car dependency [@gray2001; @shergold2012; @motte-baumvol2010].
